Nengo: A Python tool for building large-scale functional brain models

### 2013-12-04 rebuttal.txt

This is a good point. While we are currently implementing a simulator
that uses MPI, in this paper we want to highlight that Nengo is able
to simulate large networks that are typically only accessible in HPC
environments on commodity hardware. The paragraph in the introducton,
listed above, makes this explicit early on. We have also included the
following paragraph in Section 7.1:

"One key difference between Nengo's simulators and traditional neural
simulators is the target platform. While NEST and NEURON can be run on
commodity hardware, networks of modest size are typically simulated in
high-performance computing environments by using the Message-Passing
Interface (MPI). Nengo enables large-scale neural simulation on
commodity hardware, allowing researchers and hobbyists without access
to large computing clusters the ability to experiment with theoretical
neuroscience as is currently practiced in cutting edge research. In
particular, GPUs are a rich, low-cost computing resource that are
available in most modern workstations. The OpenCL simulator makes full
use of GPUs, while other simulators currently do not."

> Googling pynengo doesn't return anything, and I thought I can't find
> the package at all until I noticed that in table 1 it says that
> pynengo is the 'nengo' repository. I would advise authors making this
> more clear, to facilitate the promotion of pynengo. Perhaps end the
> introduction or discussion with clear instructions how to access the
> software.
>
> Did authors considered releasing pynengo as pypi package?

Thanks for bringing this up. As mentioned above, we have changed all
references to PyNengo to Nengo 2.0. Additionally, we have pointed to
Nengo on PyPI and Github in a footnote on page 2:

"Nengo is available for download through the Python Package Index at
https://pypi.python.org/pypi/nengo. The full source is available at
https://github.com/ctn-waterloo/nengo."

Currently, we have only registered the nengo namespace on PyPI, but we
are hoping to make an initial 2.0 release before the publication of
this paper.

> Section 7.2 about future talks about future work only in the last
> sentence.

Thank you for noticing this. We have completely rewritten Section 7.2
to more appropriately focus on future work.
